Statistical quantification of confounding bias in predictive modelling

### 2021-10-30 manuscript.tex
line numbers

Predictive modelling has recently become increasingly important in biomedical research and holds promise for delivering biomarkers that substantially impact clinical practice and public health\citep{kent2018personalized, spisak2020pain, walsh2021dome}. When evaluating the usefulness and applicability of such markers, predictive performance is far from being the only important consideration. Biomedical validity (i.e. whether the model is driven by biomedically relevant signal) as well as generalizability and fairness across contexts and populations are also fundamental requirements for candidate biomarkers\citep{woo2017building, obermeyer2019dissecting, mehrabi2021survey}.

>>>>

Predictive modelling has recently become increasingly important in biomedical research and holds promise for delivering biomarkers that substantially impact clinical practice and public health\citep{vogt2018machine, kent2018personalized, spisak2020pain, walsh2021dome}. When evaluating the usefulness and applicability of such markers, predictive performance is far from being the only important consideration. Biomedical validity (i.e. whether the model is driven by biomedically relevant signal) as well as generalizability and fairness across contexts and populations are also fundamental requirements for candidate biomarkers\citep{woo2017building, obermeyer2019dissecting, mehrabi2021survey}.
